\section{Sustainability} \label{sec:sed-ultrices}


In recent years, we have witnessed an extraordinary acceleration in the growth of artificial intelligence (AI), transforming the way we live, work, and interact with technology. AI algorithms impact sectors such as healthcare, finance, manufacturing, transportation, and entertainment. These advances are driving new chip and server technologies, resulting in extreme rack power densities and presenting new challenges in the design and operation of data centers to meet the massive demand for AI. As part of their Environmental, Social, and Governance (ESG) programs, data center operators are making commitments to environmental sustainability.\\

Data center operators should use a standard set of metrics. The Green Grid (TGG) proposed power usage effectiveness (PUE) in 2007, which was widely adopted and helped drive efficiency improvements across the industry. A global survey conducted by Uptime Institute in 2023 showed that the average annual PUE of large data centers improved from 2.5 to 1.58 since 2007.\\

Schneider Electric's growth predictions estimate that AI accounts for 8\% of the total power consumption of data centers in 2023, rising to 15-20\% by 2028. Given that data centers worldwide consumed over 500 TWh of electricity in 2023 and are projected to consume 815 TWh in 2028 (the equivalent of 16 New York Cities), AI's power consumption equates to 40 TWh in 2023 and is expected to increase to between 122 and 163 TWh by 2028.


\section{Ground Truth Data Solution}

\subsection{Approach}

At Ground Truth Data, we're tackling energy consumption in data centers with our efficient data reduction technology. This approach not only cuts down on storage space for AI data but also reduces computing times and network loads, boosting overall system efficiency.\\

Our solution brings a range of benefits: better use of storage resources, cost savings, longer hardware lifespans, and optimized data processing. For AI applications, our techniques improve performance and scalability, allowing for faster training and deployment of AI models, especially deep learning.\\

Additionally, our technology speeds up backup and recovery processes, which is crucial for the finance and healthcare sectors, and enhances the efficiency of IoT devices in edge computing. For cloud service providers, it helps meet sustainability goals and lowers operational costs.\\

Using our data reduction strategies leads to significant energy savings, lower operational costs, and greater environmental sustainability, all while maintaining high performance and reliability. Our solution also supports AI development, making AI technologies more accessible and efficient across various industries.

\subsection{Competitors}
In the competitive landscape of data reduction technology, several key players have emerged, each offering different solutions to address the growing challenges of managing and optimizing large datasets. 

\begin{itemize}
\item IBM: IBM offers various data compression and storage optimization solutions through its cloud services and software products. Their technologies focus on enhancing data efficiency and scalability for enterprises.

\item Dell Technologies: Dell provides data reduction technologies as part of its storage and data management solutions. They emphasize deduplication, compression, and encryption to improve storage efficiency and performance.

\item NetApp: NetApp specializes in data management and storage solutions, including data reduction technologies such as deduplication and compression. Their offerings are tailored for enterprise data centers and cloud environments.

\item Pure Storage: Pure Storage offers flash storage arrays with built-in data reduction features, including deduplication and compression. Their solutions target high-performance computing and enterprise storage needs.

\item Veritas Technologies: Veritas provides data management and protection solutions, including data reduction technologies for backup and storage optimization. They serve a wide range of industries with a focus on data integrity and compliance.
\end{itemize}


Our solution distinguishes itself from existing market solutions by offering a novel approach that does not rely on encryption or compression techniques. Instead, we \textbf{\textcolor{cyan}{leverage advanced algorithms that fundamentally transform how datasets are managed}}. By adopting this innovative methodology, our solution achieves a remarkable reduction in dataset size while meticulously \textbf{\textcolor{cyan}{preserving the integrity, knowledge, and critical information}} embedded within the data. 

This preservation ensures that organizations \textbf{\textcolor{cyan}{not only benefit from streamlined data storage and processing but also retain the full depth and value of their data assets}}. 

In essence, our approach sets a \textbf{\textcolor{cyan}{new standard in data management efficiency and intelligence}}, empowering businesses to optimize operations and drive informed decision-making with confidence.

\section{Results}

Ground Truth Data's solution achieves data reductions of up to 86\%, leaving only 14\% of the original data. This reduction translates to a 36\% savings in computing for AI algorithms on IoT devices and an 86\% savings in data centers.\\


Considering these figures and the optimistic consumption forecasts for data centers in the coming years, we can illustrate the potential energy and cost savings for the industry in the following table:

\begin{table}[H]
    \centering
    \footnotesize
    \begin{tabular}{|lrrrrrr}
        \toprule
        Year & AI (TWh) & Elect. price (\$) & AI Cost (B\$) & AI E. saved (TWh) & Cost saved (B\$)  & $CO_2$ saved (Mt)  \\
        \midrule
        2023 & 40  & 0.17  & 7  & 34  & 6  & 7  \\
        2024 & 54  & 0.175 & 9  & 46  & 8  & 10 \\
        2025 & 72  & 0.18  & 13 & 62  & 11 & 13 \\
        2026 & 92  & 0.185 & 17 & 79  & 15 & 16 \\
        2027 & 115 & 0.19  & 22 & 99  & 19 & 20 \\
        2028 & 143 & 0.195 & 28 & 123 & 24 & 25 \\
        2029 & 175 & 0.2   & 35 & 151 & 30 & 31 \\
        2030 & 212 & 0.206 & 44 & 182 & 38 & 38 \\
        \midrule
        & & & & 776 (TWh) & 151 (B\$) & 160 Mt $CO_2$ \\
        \bottomrule
    \end{tabular}
    \caption{}
    \label{tab:ai_summary}
\end{table}
